### 2024-07-16 Article/Article-english.tex
more

>>>>

\noindent{\it Proof.}
    Let $S^1 = \{ z \in \mathbb{C}\ | \ |z| = 1 \}$ be a~circle group, a~subgroup in~${\mathbb{C}^\times}$.
    From the~trigonometric form $z = re^{i \theta}$ we see that the~group ${\mathbb{C}^\times}$ is isomorphic
    to~the~product $\mathbb{R}_{> 0}^\times \times S^1$. The~mapping $t \mapsto e^t$ defines the~isomorphism
    of~the~groups $\mathbb{R}$ and~$\mathbb{R}_{> 0}^\times$, and the~mapping $\theta \mapsto e^{i\theta}$
    defines the~isomorphism between $\mathbb{R} / 2 \pi \mathbb{Z}$ and~$S^1$; this proves a~corollary
    by~virtue of~the~previous two lemmas.
\hfill$\Box$\medskip

\medskip\noindent\textbf{Consequence.}\emph{
    If $\phi_\alpha$ is injective over~$K = \mathbb{C}$, then~$\mathrm{rank}(\alpha) = k$.
}\medskip

\noindent{\it Proof.}
    As noted before, linear independence over~$\mathbb{R}$ is equivalent to linear independence
    in~the~vector space $\mathbb{R}^k$ over~$\mathbb{R}$, and this in turn is equivalent to having full rank.
\hfill$\Box$\medskip
